---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{shinyShortForm}`

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Codecov test coverage](https://codecov.io/gh/AnthonyRaborn/shinyShortForm/graph/badge.svg)](https://app.codecov.io/gh/AnthonyRaborn/shinyShortForm)
[![R-CMD-check](https://github.com/AnthonyRaborn/shinyShortForm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AnthonyRaborn/shinyShortForm/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Installation

You can install the development version of `{shinyShortForm}` like so:

```{r, eval = FALSE}
# require(devtools)
devtools::install_github("AnthonyRaborn/shinyShortForm")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
shinyShortForm::run_app()
```

## About

This shiny app demonstrates some of the functionality of the ShortForm R package using simulated binary response data. You can modify some of the parameters for the three metaheuristic algorithms included in the package and see example output, as well as browse the manual page for the selected algorithm.

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("shinyShortForm")
```

```{r, error = TRUE}
covr::package_coverage()
```
